Global Distribution of Unintended Pregnancies and Contraceptive Usage

### 2024-04-19 products/manuscript/Manuscript.qmd
Part 5 Updates
Minor manuscript update.

## Statistical analysis
We began with a simple linear regression model with each of the 7 predictor variables to determine the association betwen each variable and the outcome. We explored the region variable further because our main goal is to understand the difference in outcome by region. We used ANOVA to determine the difference between regions, and we added Tukey's Honeslty Significant Difference test to examine pairwise associations. This led to discovering correlations between some of the predictors, which we examined through correlation coefficients. We tried out a combination of these correlated predictors in 2 different models to further examine the interactions. After considering which predictors are most impactful on our outcome, we narrowed the final predictors down to a list of 5. We included a multiple linear regression model with all 5 of these predictors. We used the RMSE and MAE performance metrics to evaluate all 9 models that we created to determine which one fit best. Lastly, we used cross-validation to determine how well our multiple linear regression model performs on data it has not seen before. We also used LASSO regression and random forest modeling as forms of subset selection by applying a regularization penalty and generating a tree structure, respectively. Lastly, we examine the AIC values associated with our two best performing models.

>>>>

## Statistical analysis
We began with a simple linear regression model with each of the 7 predictor variables to determine the association between each variable and the outcome. We explored the region variable further because our main goal is to understand the difference in outcome by region. This led to discovering correlations between some of the predictors, which we examined through correlation coefficients. We tried out a combination of these correlated predictors in 2 different models to further examine the interactions. After considering which predictors are most impactful on our outcome, we narrowed the final predictors down to a list of 5. We included a multiple linear regression model with all 5 of these predictors. We used the RMSE and MAE performance metrics to evaluate all 9 models that we created to determine which one fit best. Lastly, we used cross-validation to determine how well our multiple linear regression model performs on data it has not seen before. We also used LASSO regression and random forest modeling as forms of subset selection by applying a regularization penalty and generating a tree structure, respectively. Lastly, we examine the AIC values associated with our two best performing models.
